---
title: "Untitled"
author: "Odwel"
date: "2023-03-01"
output: html_document
---

## Setting up my environment
Note: setting up my R environment by loading the 'tidyverse' and 'palmer 
penguins' packages


```{r loading packages}
library(tidyverse)
library(palmerpenguins)
```
### Doing some statistical calcaltion

```{r}
View(penguins)
```

```{r}
penguins %>% 
  group_by(species, island) %>% 
  drop_na() %>%
  summarise(average_flipper_length = mean(flipper_length_mm), maximum_flipper_length = max(flipper_length_mm), average_body_mass = mean(body_mass_g), maximum_body_mass = max(body_mass_g),.groups = "drop") %>% 
  arrange(species, island)
```

```{r}
penguins %>% group_by(island) %>% 
  drop_na() %>% summarise(max_bill_length_mm = max(bill_length_mm))
```
```{r}
penguins %>% group_by(species, island) %>% drop_na() %>% 
  summarise(max_bill = max(bill_length_mm), mean_bill = mean(bill_length_mm),.groups = "drop")
```

## Visualizations
Here, we will go through a series of visualizations


### Flipper and Body mass in Purple
Here, we plot flipper length against body mass 


```{r visualize flipper and body mass in purple}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g), color = "Purple")
```


### Flipper and body mass by species
Here, we plot flipper length against body and look at the breakdown by 
species


```{r species}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, shape = species, color = species))
```


### Flipper and body mass by species and sex
Here, we plot flipper length against body mass and look at the breakdown by
species and sex 


```{r species and sex}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g, color = species, shape = species)) + 
  facet_wrap(~sex)
```












